Security vs. Maintainability: \\ Fixing Vulnerabilities Obfuscates your Code

### 2019-01-28 paper/ICPC19/icpc19.tex
minor fixes

\usepackage{pifont}
\newcommand{\lstbg}[3][0pt]{{\fboxsep#1\colorbox{#2}{\strut #3}}}
\lstset{ %
  language=C,
  backgroundcolor=\color{white},   % choose the background color
  basicstyle=\ttfamily\scriptsize,        % size of fonts used for the code
  breaklines=true,                 % automatic line breaking only at whitespace
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygray}\bfseries,    % comment style
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  keywordstyle=\color{blue},       % keyword style
  stringstyle=\color{mymauve},     % string literal style
  frame=single,
  numbers=left,
  stepnumber=1,
  xleftmargin=2em,
  escapeinside={/*!}{!*/},
  moredelim=**[l][\color{mygreen}]{+},
  moredelim=*[l][\color{red}]{-}
}

@@

\setcounter{lstannotation}{0}
\begin{lstlisting}[caption={Fix provided by OpenSSL developers to the CVE-2014-3506 vulnerability \Sof{@todo: Fix the regex issue}},label={lst:vuln}]
+static unsigned long dtls1_max_handshake_message_len(const SSL *s){ /*!\annotation{lst:func1}!*/
+
+ unsigned long max_len = DTLS1_HM_HEADER_LENGTH + SSL3_RT_MAX_ENCRYPTED_LENGTH;
+ if(max_len < (unsigned long)s->max_cert_list) /*!\annotation{lst:func2}!*/
+    return s->max_cert_list;
+ return max_len;
+}

@@

- unsigned long frag_len = msg_hdr->frag_len, max_len; /*!\annotation{lst:func3}!*/
-
- if((msg_hdr->frag_off+frag_len) > msg_hdr->msg_len)
-    goto err;

- if(DTLS1_HM_HEADER_LENGTH + SSL3_RT_MAX_ENCRYPTED_LENGTH < s->max_cert_list)
-    max_len = s->max_cert_list;
- else
-    max_len = DTLS1_HM_HEADER_LENGTH + SSL3_RT_MAX_ENCRYPTED_LENGTH;

@@

\subsection{Statistical Validation}\label{sec:statsval}
%
To validate the maintainability differences in different groups of commits
(e.g., baseline and security commits), we use the Paired Wilcoxon signed-rank
test with the significance level $\alpha = 0.05$ \cite{10.2307/3001968} . In
other words, we test the null hypothesis that the maintainability difference
between pairs of versions $v_{v-1}$, $v_v$ (i.e., before and after a
security-commit) follows a symmetric distribution around $0$. However, when the
difference between groups is zero, the observations are discarded. Thus, we use
a more robust approach of the wilcoxon test, the Wilcoxon test by Pratt which
provides an alternative that incorporates the cases where the maintainability
difference is zero \cite{10.2307/2282543}. To understand the effect-size, as
advocated by the Common-language effect sizes \cite{graw:1992}, we compute the
mean difference, the median of the difference, and the percentage of cases that
reduce maintainability.
%
\section{Results}\label{sec:results}

@@

@@

\begin{figure}[h]
 	\centering
 	\includegraphics[width=0.45\textwidth]{figures/maintainability.pdf}
 	\caption{Maintainability difference for security and baseline refactorings}
	\label{fig:secvsreg}
\end{figure}

>>>>

\usepackage{pifont}
\newcommand{\lstbg}[3][0pt]{{\fboxsep#1\colorbox{#2}{\strut #3}}}
\lstset{ %
  language=C,
  backgroundcolor=\color{white},   % choose the background color
  basicstyle=\ttfamily\scriptsize,        % size of fonts used for the code
  breaklines=true,                 % automatic line breaking only at whitespace
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygray}\bfseries,    % comment style
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  keywordstyle=\color{blue},       % keyword style
  stringstyle=\color{mymauve},     % string literal style
  frame=single,
  numbers=left,
  stepnumber=1,
  xleftmargin=2em,
  escapeinside={/*!}{!*/},
  moredelim=**[l][\color{mygreen}]{+\ },
  moredelim=*[l][\color{red}]{-\ }
}

@@

\setcounter{lstannotation}{0}
\begin{lstlisting}[caption={Fix provided by OpenSSL developers to the CVE-2014-3506 vulnerability \Sof{@todo: Fix the regex issue}},label={lst:vuln}]
+ static unsigned long dtls1_max_handshake_message_len(const SSL *s){ /*!\annotation{lst:func1}!*/
+  unsigned long max_len = DTLS1_HM_HEADER_LENGTH + SSL3_RT_MAX_ENCRYPTED_LENGTH;
+  if(max_len < (unsigned long)s->max_cert_list) /*!\annotation{lst:func2}!*/
+     return s->max_cert_list;
+  return max_len;
+ }

@@

- unsigned long frag_len = msg_hdr->frag_len, max_len; /*!\annotation{lst:func3}!*/

- if((msg_hdr->frag_off+frag_len) > msg_hdr->msg_len)
-    goto err;

- if(DTLS1_HM_HEADER_LENGTH +
-    	SSL3_RT_MAX_ENCRYPTED_LENGTH < s->max_cert_list)
-    max_len = s->max_cert_list;
- else
-    max_len = DTLS1_HM_HEADER_LENGTH +
-   		SSL3_RT_MAX_ENCRYPTED_LENGTH;

@@

\subsection{Statistical Validation}\label{sec:statsval}
%
To validate the maintainability differences in different groups of commits
(e.g., baseline and security commits), we use the Paired Wilcoxon signed-rank
test with the significance level $\alpha = 0.05$ \cite{10.2307/3001968} . In
other words, we test the null hypothesis that the maintainability difference
between pairs of versions $v_{v-1}$, $v_v$ (i.e., before and after a
security-commit) follows a symmetric distribution around $0$. However, when the
difference between groups is zero, the observations are discarded. Thus, we use
a more robust approach of the wilcoxon test, the Wilcoxon test by Pratt which
provides an alternative that incorporates the cases where the maintainability
difference is zero \cite{10.2307/2282543}. To understand the effect-size, as
advocated by the Common-language effect sizes \cite{graw:1992}, we compute the
mean difference, the median of the difference, and the percentage of cases that
reduce maintainability.

%
\section{Results}\label{sec:results}

@@

The impact of security and baseline commits in the maintainability of open-source software is presented in Figure \ref{fig:secvsreg}. For each type of change, three types of impact of refactorings in the software maintainability are presented: \emph{negative}, i.e., maintainability decreased (\emph{red}); \emph{none}, i.e., the maintainability did not suffer any changes (\emph{yellow}); and, \emph{positive}, i.e., the maintainability increased (\emph{negative}).

\begin{figure}[h]
 	\centering 	\includegraphics[width=0.5\textwidth]{figures/maintainability.pdf}
 	\caption{Maintainability difference for security and baseline refactorings}
	\label{fig:secvsreg}
\end{figure}

@@
